Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-08-23 paper/ms.tex
more text on the results section

Figure \ref{fig:landscape} presents regions in parameter space $M_{\rm
min}-M_{\rm max}$, $M_{\rm min}-f_{\rm occ}$ where the KS test yields
values of $P>0.05$ at least for one mock survey. For those models it
is not possible reject the hypothesis that the simulated and observed
data for the surface number density come from the same parent
distribution. In total, there are between $550$ to $600$ models out of
the original $9000$ models that have at least one mock survey
consistent with observations.

@@

For each model ${\mathcal M}$ there are 15 different mock surveys. In the
previous section we presented the models that had at least one
mock survey with $P>0.05$. Figure \ref{fig:high_success_rate} shows the number of models
that have at least $N_{\rm high-P}$ mocks with $P>0.05$ for both the
{\texttt  match} and {\texttt random} methods.  This shows that there
are $\sim 100$ models with all the 15 mock survey realizations with
$P>0.05$.

We discard the models that have 14 mocks or less consistent with observations.
This cut represents a reduction by a factor of $\sim 6$ with respect
to the total number of models with at least one (1) consistent mock.

@@

@@

>>>>

Figure \ref{fig:landscape} presents regions in parameter space $M_{\rm
min}-M_{\rm max}$, $M_{\rm min}-f_{\rm occ}$ where the KS test yields
values of $P>0.05$ at least for one mock survey, which is the most
conservative assumption for agreement between a model and observations. For those models it
is not possible reject the hypothesis that the simulated and observed
data for the surface number density come from the same parent
distribution. In total, there are between $550$ to $600$ models out of
the original $9000$ models that have at least one mock survey
consistent with observations. By inspection of Figure
\ref{fig:landscape} we see that the halo number abundance is able to
constraint the minimum mass $M_{\rm min}$ to a narrow range, while
$M_{\rm max}$ and $f_{\rm occ}$ remain unconstrained.

@@

In the previous Section we present a conservative criterion of
agreement by selecting the models that had at least one mock survey
with $P>0.05$ in the KS test. Now we turn to a more strict selection
by requiring all constructed mock surveys to be consistent with
observations.

Figure \ref{fig:high_success_rate} shows the number of models
that have at least $N_{\rm high-P}$ mocks with $P>0.05$. For each
model ${\mathcal M}$ there are 15 different mock surveys.  We discard
the models that have 14 mocks or less consistent with
observations. With this cut we find $\sim 100$ models with all the 15
mock survey realizations with $P>0.05$.  This cut represents a
reduction by a factor of $\sim 6$ with respect to the total number of
models with at least one consistent mock.

@@

We conclude that conditions on the number density statistics, even if they are
very strict, only put strong constraints on the minimum mass $M_{\rm
  min}$ but not on the other two parameter of the model $M_{\rm max}$
and $f_{\rm occ}$. In the next section we use additional observational
information to constrain these paremeters.

@@

We conclude that the clustering information is able to put meaningful
constraints on the values of the maxium mass parameters $M_{\rm max}$
and the occupation fraction $f_{\rm occ}$.
